---
title: "Lab 07 - Modelling course evaluations"
author: "INSERT NAME HERE"
date: "`r Sys.Date()`"
output: html_document
---

### Packages and Data

```{r load-packages, message=FALSE, echo=TRUE}
library(tidyverse)
library(tidymodels)

```


```{r read-data}
evals<-read.csv("data/evals.csv", row.names=1)
```


# Exercise 1: Exploratory Data Analysis

1.  Visualize the distribution of `score` in the dataframe `evals`.

```{r viz-score}
evals %>% ggplot() + geom_histogram(mapping = aes(x = score))

evals %>% group_by(gender) %>% summarize(mean = mean(score))
```

*So clearly students are more likely to give their teachers a better rating. Also the male teachers genreally got a better rating on average.*

2.  Visualize and describe the relationship between `score` and `bty_avg` using `geom_point()` to represent the data. 

```{r scatterplot}
evals %>% ggplot() + geom_point(mapping = aes(x = bty_avg, y = score))

evals %>% ggplot() + geom_jitter(mapping = aes(x = bty_avg, y = score))
```

*The jitter adds random noise to the points. In the first plot many of the points lie on the same line since people will generally give "nice" numbers as a score*

# Exercise 2: Simple Linear regression with a numerical predictor

1. Fit a linear model called `score_bty_fit` to predict average professor evaluation `score` from average beauty rating (`bty_avg`). Print the regression output using `tidy()`.

```{r fit-score_bty_fit, eval = FALSE}
# remove eval = FALSE from the code chunk options after filling in the blanks
score_bty_fit <- linear_reg() %>%
  set_engine("lm") %>%
  fit(score ~ bty_avg, data = evals)

tidy(score_bty_fit)

```

*score = 0.667bty_avg + 3.88 hence for a teacher with "0" beuty they will still have a score of 3.88*

2. Plot the data again using `geom_jitter()`, and add the regression line.

```{r viz-score_bty_fit,eval=FALSE}
evals %>% ggplot() + geom_jitter(mapping = aes(x = bty_avg, y = score)) + geom_smooth(method = "lm", se = FALSE, mapping = aes(x = bty_avg, y = score))
```

3. Interpret the slope of the linear model in context of the data.

*Beuty and score are directly proportional*

4. Interpret the intercept of the linear model in context of the data. Comment on whether or not the intercept makes sense in this context.

*So clearly the baseline score for teaching is 3.88 despite beuty*

5. Determine the $R^2$ of the model and interpret it in the context of the data.

```{r R2}
# remove eval = FALSE from the code chunk options after filling in the blanks
glance(score_bty_fit)$r.squared
```

*The linear regression is not very reliable and so is clearly not a very good fit*

6. Make a plot of residuals vs. predicted values for the model above.

```{r viz-score_bty_fit-diagnostic}
# remove eval = FALSE from the code chunk options after filling in the blanks
score_bty_aug <- augment(score_bty_fit$fit)

ggplot(data = score_bty_aug) + geom_point(mapping = aes(x = .fitted, y = .resid) )
```

# Exercise 3: Simple Linear regression with a categorical predictor

0. Look at the variable rank, and determine the frequency of each category level.

```{r}
ggplot(data = evals) + geom_bar(mapping = aes(x = rank))
```

1. Fit a new linear model called `score_rank_fit` to predict average professor evaluation `score` based on `rank` of the professor.

```{r fit-score_rank_fit}
# fit model
score
# tidy model output
```

*Add your narrative here.*

2. Fit a new linear model called `score_gender_fit` to predict average professor evaluation `score` based on `gender` of the professor. 

```{r fit-score_gender_fit}
# fit model
score_gender_fit <- linear_reg() %>%
  set_engine("lm") %>%
  fit(score ~ gender, data = evals)

tidy(score_gender_fit)
# tidy model output
```

```{r score_gender_intercept}
# remove eval = FALSE from the code chunk options
score_gender_intercept <- tidy(score_gender_fit) %>% 
  filter(term == "(Intercept)") %>%
  select(estimate) %>%
  pull()
```

```{r score_gender_slope, eval=FALSE}
# remove eval = FALSE from the code chunk options
score_gender_slope <- tidy(score_gender_fit) %>% 
  filter(term == "gendermale") %>%
  select(estimate) %>%
  pull()
```

The intercept of the model is `r round(score_gender_intercept,2)`

# Exercise 4: Multiple linear regression

1. Fit a multiple linear regression model, predicting average professor evaluation `score` based on average beauty rating (`bty_avg`) and `gender.`

```{r fit-score_bty_gender_fit}
# fit model
score_gender_bty_fit <- linear_reg() %>%
  set_engine("lm") %>%
  fit(score ~ gender + bty_avg, data = evals)

 tidy(score_gender_bty_fit)
# tidy model output
```

score = 3.75 + 0.172Male + 0.074bty_avg

```{r eval = FALSE}
evals %>% group_by(gender) %>% ggplot() + geom_smooth(method = "lm", se = FALSE, mapping = aes(x = bty_avg, y = score))
```

2. What percent of the variability in `score` is explained by the model `score_bty_gender_fit`. 

```{r}
#
```


3. What is the equation of the line corresponding to just male professors?

*Add your equation here.*

4. For two professors who received the same beauty rating, which gender tends to have the higher course evaluation score?

*Add your narrative here.*

5. How does the relationship between beauty and evaluation score vary between male and female professors?

*Add your narrative here.*

6. How do the adjusted $R^2$ values of `score_bty_fit` and `score_bty_gender_fit` compare? 

```{r eval=FALSE}
# remove eval = FALSE from the code chunk options after filling in the blanks
glance(___)$adj.r.squared
glance(___)$adj.r.squared
```

*Add your narrative here.*

7. Compare the slopes of `bty_avg` under the two models (`score_bty_fit` and `score_bty_gender_fit`).

*Add your narrative here.*

# Exercise 5: Interpretation of log-transformed response variables

If you do not know how to use LaTeX, do this exercise with pen and paper.
